Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-16 paper/main.tex
Added short intro to Technical Procedure

%**************************************%
\chapter{Procedure}
%**************************************%

% FIXME: A more descriptive/better chapter title
%
%A bit more technical description of how we tested the candidates in Tahoe-LAFS
% - Limitations/assumptions
% - Optimized candidates.
% - Error sources.
% The points above should be taken into consideration on each section in this
% chapter.

In this chapter we will outline the procedure followed to complete our task.
% TODO: Mer intro

@@

\section{Modifications in the Tahoe-\ac{LAFS} Code}

>>>>

%**************************************%
\chapter{Technical Procedure}
%**************************************%

% FIXME: A more descriptive/better chapter title?
%
%A bit more technical description of how we tested the candidates in Tahoe-LAFS
% - Limitations/assumptions
% - Optimized candidates.
% - Error sources.
% The points above should be taken into consideration on each section in this
% chapter.

In this chapter we will outline the procedure followed to complete our work.
Although not carried out sequentially, the problem was split up to the
following parts:

\begin{enumerate}
  \item Choose the best suiting implementations of the SHA-3 candidates.
  \item Write Python bindings, with unit tests for verification, to be able to
    use the functions from Python.
  \item Modify the Tahoe-LAFS code to utilize the SHA-3 functions.
  \item Create a method of distributing new code fast and easy to the test grid.
  \item Set up the test environment and choose test vectors.
\end{enumerate}

@@

\section{Modifications to the Tahoe-\ac{LAFS} Code}
